---
title: "Figures"
format: html
---


```{r}
library(readxl)
library(tidyverse)
theme_set(theme_light())

df <- readxl::read_excel("data/output/dbscan_clusters_business_counts.xlsx")

df <- df %>% 
mutate(foundation_year = parse_number(foundation_year),
financials_capital = parse_number(financials_capital),
financials_annual_turnover = parse_number(financials_annual_turnover))

# Define the dictionary
cluster_labels <- c("Glass & Mirror Factories",
                    "Spinning, weaving and textile industry",
                    "Iron and Steel Foundries",
                    "Chemical-technical industry, Chemical and pharmaceutical products, Paint and varnish factories",
                    "Various family owned businesses",
                    "Steel and metal industry",
                    "Building contractor, Concrete goods factory",
                    "Mechanical workshops for machine production (heavy industries)",
                    "Wood, sawmill and carpentry industry",
                    "Textile and leather processing industry",
                    "Book Printing and Publishing",
                    "Information Not Available",
                    "Metal goods factory, Mechanical workshop (light industries)",
                    "Preserved and fresh food industries",
                    "Food industry",
                    "Furniture and homeware factories",
                    "Breweries, malt and soft drink factories",
                    "Chemical-technical industry and jewellery",
                    "Electrical appliances and mechanical machinery",
                    "Clothing and textile industry")

# Create a dataframe
cluster_labels <- cluster_labels %>% 
    as_tibble() %>% 
    mutate(cluster = row_number() - 1) %>% 
    rename(cluster_label = value)

df <- df %>% 
inner_join(cluster_labels, by = "cluster") 
```


```{r}
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("IBM Plex Mono", "ibm")
font_add_google("Roboto", "roboto")

showtext_opts(dpi = 300)
showtext_auto(enable = TRUE)
```

## Maps

```{r}
library(sf)

maps_path <- "data/maps/sweden_24_couties.shp"

# Read in the shapefile
sweden <- st_read(maps_path)
```


```{r}
df %>% 
ggplot(aes(x = foundation_year, fill = cluster_label)) +
geom_density(show.legend = FALSE) +
facet_wrap(~cluster_label) +
scale_x_continuous(limits = c(1850, 1947)) 

```


## geom density plot

```{r}
library(ggridges)

order_cluster <- df %>% 
filter(
between(foundation_year, 1800, 1950)
) %>% 
    count(foundation_year, cluster_label) %>%
    group_by(cluster_label) %>%
    slice_max(n, n = 1, with_ties = FALSE) %>%
    ungroup() %>%
    arrange(foundation_year) %>%
    select(cluster_label) %>%
    mutate(row_num = row_number())

df %>% 
filter(cluster_label != "Information Not Available") %>%
inner_join(order_cluster, by = c("cluster_label")) %>% 
filter(
    #cluster_label %in% top_10_sectors$cluster_label,
between(foundation_year, 1800, 1950)) %>%
mutate(cluster_label = fct_reorder(cluster_label, -row_num)) %>%
mutate(foundation_year = foundation_year %/% 3 * 3) %>%
count(cluster_label, foundation_year)  %>% 
ggplot(aes(x = foundation_year, y = cluster_label, height = n, fill = cluster_label)) +
geom_density_ridges(stat = "identity", show.legend = F) +
scale_x_continuous(limits = c(1800, 1947)) +
labs(x = "Foundation year",
y = NULL) 

ggsave("figures/geom_density_ridges.png", width = 20, height = 20, units = "cm")
```

```{r}

```

```{r}

df %>% 
# create 5 year period to average over
mutate(foundation_year = foundation_year %/% 5 * 5) %>%
group_by(cluster_label, foundation_year) %>%
summarise(n = n()) %>%
ungroup() %>%
count(cluster_label, foundation_year) %>% ggplot(aes(x = foundation_year, y = n, fill = cluster_label)) +
geom_area(show.legend = FALSE, position = "fill") +
scale_x_continuous(limits = c(1850, 1947)) 


```

```{r}
top_10_sectors <- df %>% 
count(cluster_label, sort = T) %>% 
head(10)


df %>% 
filter(cluster_label %in% top_10_sectors$cluster_label) %>%
ggplot(aes(coordinates_Longitude, coordinates_Latitude, colour = cluster_label)) +
geom_point() +
labs(colour = "Most common business by region") +
facet_wrap(~cluster_label) +
scale_color_brewer(palette = "Paired") 
```

```{r}

most_common_business_labels <- cluster_labels %>% 
rename(most_common_business_label = cluster_label,
       most_common_business = cluster) 

df %>% 
inner_join(most_common_business_labels) %>% 
ggplot(aes(coordinates_Longitude, coordinates_Latitude, colour = most_common_business_label)) +
geom_point() +
labs(colour = "Most common business by region") +
# facet_wrap(~dbscan_cluster) +
scale_color_brewer(palette = "Paired") 

```


## Map with common business by region

```{r}
df_map <- df %>% 
inner_join(most_common_business_labels)


ggplot() +
geom_sf(data = sweden, fill = "grey90", color = "black") +
geom_point(aes(coordinates_Longitude, coordinates_Latitude, colour = most_common_business_label), data = df_map) +
labs(colour = "Most common business by region") +
# facet_wrap(~dbscan_cluster) +
scale_color_brewer(palette = "Paired") +
labs(x = NULL,
y = NULL)

ggsave("figures/map_most_common_businesses.png", width = 30, height = 20, units = "cm")

```



```{r}
most_specific_business_labels <- cluster_labels %>% 
rename(most_specific_business_label = cluster_label,
       most_specific_business = cluster) 


df_map <- df %>%
inner_join(most_specific_business_labels)


ggplot() +
geom_sf(data = sweden, fill = "grey90", color = "black") +
geom_point(aes(coordinates_Longitude, coordinates_Latitude, colour = most_specific_business_label), data = df_map) +
labs(colour = "Most specific business by region") +
# facet_wrap(~dbscan_cluster) +
scale_color_brewer(palette = "Set1") 

```


### Capital vs employees

We can say that the electronics industry is more capital intensive than other industries.


```{r}
df %>% 
mutate(electronics_flag = ifelse(cluster_label == "Electrical appliances and mechanical machinery", "Electronics", "Other")) %>%
filter(financials_capital > 0,
financials_employees_total > 0) %>%
ggplot(aes(financials_capital, financials_employees_total, colour = electronics_flag)) +
geom_point() +
geom_smooth(method = "lm", se = FALSE) +
scale_x_log10() +
scale_y_log10() 
```


Run a linear regression to see if there is a difference in the slope of the line between the two groups.

```{r}
library(broom)
library(knitr)

df %>%
mutate(electronics_flag = ifelse(cluster_label == "Electrical appliances and mechanical machinery", "Electronics", "Other")) %>%
filter(financials_capital > 0,
financials_employees_total > 0) %>%
group_by(electronics_flag) %>%
do(tidy(lm(financials_employees_total ~ financials_capital, data = .))) %>%
filter(term == "financials_capital") %>%
select(electronics_flag, estimate, p.value) %>%
mutate(p.value = round(p.value, 3)) %>%
rename(slope = estimate) %>%
kable()
```


```{r}
library(broom)
library(knitr)

df %>%
mutate(mech_flag = ifelse(cluster_label == "Mechanical workshops for machine production (heavy industries)", "Mechanical workshops", "Other")) %>%
filter(financials_capital > 0,
financials_employees_total > 0) %>%
ggplot(aes(financials_capital, financials_employees_total, colour = mech_flag)) +
geom_point() +
geom_smooth(method = "lm", se = FALSE) +
scale_x_log10() +
scale_y_log10() 
```


We can say that the electronics industry is no more capital intensive than other industries, whereas the mechanical workshops are more.

```{r}
df %>%
mutate(flag = case_when(
    cluster_label == "Mechanical workshops for machine production (heavy industries)" ~ "Mechanical workshops", 
    cluster_label == "Electrical appliances and mechanical machinery" ~ "Electrical appliances and mechanical machinery",
    TRUE ~ "Other")) %>%
filter(financials_capital > 0,
financials_employees_total > 0) %>%
ggplot(aes(financials_capital, financials_employees_total, colour = flag)) +
geom_point(alpha = .5) +
geom_smooth(method = "lm", se = FALSE) +
scale_color_brewer(palette = "Dark2") +
scale_x_log10(labels = scales::dollar_format(prefix = "SEK ")) +
scale_y_log10(limits = c(NA, 1e4), labels = scales::number_format(big.mark = ",")) +
labs(colour = "Firm type",
x = "Stock of financial capital (log scale)",
y = "Number of employees (log scale)") +
theme(legend.position = "bottom") +
coord_cartesian()

ggsave("figures/capital_vs_employees.png", width = 20, height = 20, units = "cm")
```



Rerun this analysis for every cluster lable and see if it is more capital intensive than other industries.

```{r}
library(broom)
library(knitr)

df %>%
mutate(electronics_flag = ifelse(cluster_label == "Electrical appliances and mechanical machinery", "Electronics", "Other")) %>%
filter(financials_capital > 0,
financials_employees_total > 0) %>%
group_by(cluster_label) %>%
do(tidy(lm(financials_employees_total ~ financials_capital, data = .))) %>%
filter(term == "financials_capital") %>%
select(cluster_label, estimate, p.value) %>%
mutate(p.value = round(p.value, 3)) %>%
rename(slope = estimate) %>%
arrange(desc(slope)) %>%
kable()

```

The most capital intensive industries are Mechanical workshops for machine production (heavy industries), as well as Iron and Steel Foundries.




What about the power station


```{r}

library(ggrepel)

df %>% 
filter(str_detect(business, "kraft|elektr"))   %>% view()


df_map <- df %>% 
filter(str_detect(business, "kraft|elektr"))  %>% 
mutate(
    firm_type = case_when(
        str_detect(business, "kraft") ~ "Power station / supply company",
        str_detect(business, "elektr") ~ "Electronic products company",
    )
) 


ggplot() +
geom_sf(data = sweden, fill = "grey90", color = "black") +
geom_point(aes(coordinates_Longitude, coordinates_Latitude, size = financials_capital, colour = firm_type), data = df_map) +
geom_text_repel(aes(coordinates_Longitude, coordinates_Latitude, label = name), size = 2, check.overlap = TRUE, data = df_map) +
scale_colour_brewer(palette = "Dark2") +
scale_size_continuous(labels = scales::dollar_format(prefix = "SEK ")) +
labs(colour = "Firm type",
size = "Stock of financial capital",
x = NULL, 
y = NULL)


ggsave("figures/map_of_electricity_related_businesses.png", width = 20, height = 20, units = "cm")
```






## Animated map of business locations over time

```{r}

df %>% 
ggplot(aes(coordinates_Latitude, coordinates_Longitude, colour = foundation_year)) 

```



```{r}
library(ggthemes)
library(gganimate)
library(gifski)


df %>% select(cluster_label)  %>% distinct()



df_gif <- df %>%
select(name, location, financials_capital, financials_annual_turnover, financials_employees_total, coordinates_Latitude, coordinates_Longitude, foundation_year, cluster_label) %>%
mutate(end = 1947,
# mutate(financials_info = case_when(
#     is.na(financials_capital) & is.na(financials_annual_turnover) ~ NA_real_,
#     is.na(financials_capital) ~ financials_annual_turnover,
#     is.na(financials_annual_turnover) ~ financials_capital,
#     TRUE ~ sum(financials_capital, financials_annual_turnover, na.rm = TRUE)
# ))
foundation_year = case_when(
    foundation_year < 1800 ~ NA_real_,
    foundation_year > 1947 ~ 1947,
    TRUE ~ foundation_year
),
cluster_type = case_when(
    cluster_label == "Electrical appliances and mechanical machinery" ~ "Electronics",
    cluster_label %in% c("Mechanical workshops for machine production (heavy industries)", "Metal goods factory, Mechanical workshop (light industries)") ~ "Mechanical workshops",
    # textile and clothing 
    cluster_label %in% c("Spinning, weaving and textile industry", "Clothing and textile industry", "Textile and leather processing industry") ~ "Textile and clothing",
    TRUE ~ "Other industries"),
cluster_type = fct_relevel(cluster_type, "Electronics", "Mechanical workshops", "Textile and clothing", "Other industries")) %>% 
mutate(foundation_year = case_when(
    cluster_type == "Electronics" & foundation_year < 1890 ~ NA_real_,
    TRUE ~ foundation_year
)) %>%
filter(foundation_year <= 1947,
!is.na(foundation_year)) %>%
mutate(year = map2(foundation_year, end, seq)) 

df_gif <- df_gif %>%
unnest(year) 

p <- df_gif %>% 
  ggplot(aes(coordinates_Longitude, coordinates_Latitude, colour = cluster_type)) +
  geom_point(size = .25, alpha = .25) +
  transition_manual(year) +
  labs(title = "Establishment of industrial firms in Sweden: Year { current_frame }",
       colour = "Post Office Established",
       caption = "Data: Swedish Industrial Firm Calendar 1947") +
  theme_map() +
  coord_map() +
  facet_wrap(~cluster_type, nrow = 1) +
  scale_colour_brewer(palette = "Dark2") +
  theme(plot.title = element_text(hjust = .5),
        legend.position = "none",
        # text size smaller
        text = element_text(size = 5), 
        ) +
  guides(colour = guide_colorbar(barwidth = 30, 
                                 barheight = 1, 
                                 title.position = "top", 
                                 title.hjust = .5)) 

animate(p, renderer = av_renderer(file = "figures/establishment-ep_sq.mp4"),
           width = 1080,
           heigh = 720,
        res = 360,
        duration = 60,
        end_pause = 55
        )



```



```{r}
df_gif %>% filter(!cluster_type == "Electronics") %>%
arrange(foundation_year) %>% 
select(name, foundation_year, cluster_type) %>%
distinct() 


df_gif %>% 
ggplot(aes(foundation_year)) +
geom_histogram()
```



## Now we make calculations based on whether these are in the treatment or control group



```{r}
library(here)
library(sf)

counties <- st_read(here::here("data", "maps", "sweden_24_couties.shp"))

counties <- counties %>%
mutate(year = map2(1800, 1947, seq)) %>%
unnest(year)

parishes_subset_treated <- 
  st_read(here::here("data", "maps", "parishes_subset_treated.shp"))

parishes_subset_treated = parishes_subset_treated %>% 
mutate(year = map2(1800, 1947, seq)) %>%
unnest(year)

parishes_subset_control <-
    st_read(here::here("data", "maps", "parishes_subset_control.shp"))

parishes_subset_control = parishes_subset_control %>% 
mutate(year = map2(1800, 1947, seq)) %>%
unnest(year)

df_gif %>% 
  ggplot() +
  geom_sf(data = parishes_subset_treated, fill = "grey90", color = "black") +
  geom_point(size = .25, alpha = .25, aes(coordinates_Longitude, coordinates_Latitude, colour = cluster_type))


p <- df_gif %>% 
  ggplot() +
    geom_sf(data = counties, color = "black", alpha = .3, fill = NA) +
  geom_sf(data = parishes_subset_treated, color = NA, alpha = .7, aes(fill = "Treated parishes")) +
  geom_sf(data = parishes_subset_control, color = NA, alpha = .7, aes(fill = "Control parishes")) +
  geom_point(size = .5, alpha = .8, aes(coordinates_Longitude, coordinates_Latitude, colour = cluster_type)) +
    scale_fill_manual(
    values = c("Treated parishes" = "#fc8d59", "Control parishes" = "#fef0d9"),
    guide = guide_legend(override.aes = list(linetype = "blank", shape = NA))
  ) +
  transition_manual(year) +
  labs(title = "Establishment of industrial firms in Sweden: Year { current_frame }",
       colour = "Post Office Established",
       caption = "Data: Swedish Industrial Firm Calendar 1947",
       fill = "Parish type") +
  theme_map() +
  coord_sf() +
  # coord_map() +
  facet_wrap(~cluster_type, nrow = 1) +
  scale_colour_brewer(palette = "Dark2") +
  theme(plot.title = element_text(hjust = .5),
        legend.position = "bottom",
        # text size smaller
        text = element_text(size = 5), 
        ) +
  guides(colour = guide_colorbar(barwidth = 30, 
                                 barheight = 1, 
                                 title.position = "top", 
                                 title.hjust = .5)) 

animate(p, renderer = av_renderer(file = "figures/establishment-ep_sq.mp4"),
           width = 1400,
           heigh = 1000,
        res = 360,
        duration = 60,
        end_pause = 10
        )



```





```{r}
# use coordinates_Longitude and coordinates_Latitude to create a point geometry
df_sf <- st_as_sf(df %>% 
filter(!is.na(coordinates_Longitude), !is.na(coordinates_Latitude)), coords = c("coordinates_Longitude", "coordinates_Latitude"))

# set df_sf to the same CRS as the parishes
df_sf <- st_transform(df_sf, st_crs(parishes_subset_treated))


df_sf %>% 
st_filter(parishes_subset_treated)

```